\mbox{Specifying Imperative Higher Order Programs}

### 2009-09-28 papers/esop2010/main.tex
little change

Again in order to simplify future definitions, the definition typing relation
differs somewhat from the standard way (see Fig.\ref{fig:typing}). First of
all, we present the language in {\em A-normal form} (ANF), where all values
obtained by intermediate computations are named. However, our definition of
values is not syntactical: our ``semantic'' values are objects which are
either syntactic values (abstractions and variables) or are obtained by {\em
pure application}, the application which involves the pure arrow $->$.
Furthermore, the system is a type and effect system. There are in fact two
typing relations, the first one is of the form $Γ|-_v : t : τ$. In this case,
$t$ is a semantic value of type $τ$ and cannot have any effect. In the other
case, we have $Γ|- : t : τ, ε$, where $t$ is an expression of type $τ$ and
effect $ε$.

Effects can be produced only by function application.

>>>>

Again in order to simplify future definitions, the definition typing relation
differs somewhat from the standard way (see Fig.\ref{fig:typing}). First of
all, we present the language in {\em A-normal form} (ANF), where all values
obtained by intermediate computations are named. However, our definition of
values is not syntactical: our ``semantic'' values are objects which are
either syntactic values (abstractions and variables) or are obtained by {\em
pure application}, the application which involves the pure arrow $τ->τ$.
Furthermore, the system is a type and effect system. There are in fact two
typing relations, the first one is of the form $Γ|-_v : t : τ$. In this case,
$t$ is a semantic value of type $τ$ and cannot have any effect. In the other
case, we have $Γ|- : t : τ, ε$, where $t$ is an expression of type $τ$ and
effect $ε$.

Effects can be produced only by function application, where the impure arrow
$τ->^ετ$ is involved.
